---
title: "Lab 05: harvesting research data"
author: "Abby Komiske"
date: 2024-02-28
date-modified: today
format: 
  html:
    toc: true
---

## Data description 

<!--

the nature of the data
  - the source of the data
  - the acquisition strategy that will be used
  - the format of the data
  - the license of the data
  
-->

The data that I am downloaidng is the Switchboard Dialog Act Corpus. This corpus is a set of interviews. 

The data is in an archived file on the [LDC](https://catalog.ldc.upenn.edu/docs/LDC97S62). In this case, I am going to download, unarchive, and save the contents of teh corpus to the 'data/original/swda' / directory. 

<!-- Note to self: the path from the current file is: '../data/original/swda' -->

```{r}
#| label: setup-packages
#| message: false 

#| Load packages 
library(dplyr)
library(fs)

```

The first step in the process it to try out using 'download.file()' to acquire the archived file.

```{r}
#|label: download-archive-test

# URL : https://catalog.ldc.upenn.edu/docs/LDC97S62/swb1_dialogact_annot.tar.gz

# Set 'url' to the file address 
file_url <- "https://catalog.ldc.upenn.edu/docs/LDC97S62/swb1_dialogact_annot.tar.gz" 

dest_directory <- "../data/original/swda.tar.gz"

download.file (url = file_url, destfile = dest_directory)

```

Now the file is at '../data/original/swda.tar.gz'. Since it is an archived file, I will need to unarchive it. It's extension is 'tar.gz' so I will use the 'untar()' function from the base R. 

```{r}
#| label: unarchive-tes 

untar(tarfile = "../data/original/swda.tar.gz", exdir = "../data/original/swda/")

```


## Displaying the data

Now I can display the data as a table. 

```{r}
qtalrkit :: create_data_origin ()
```





